An Efficient Forecasting Approach\\ to Reduce Boundary Effects in Real-Time Time-Frequency Analysis

### 2021-01-24 Paper/Supplementary material/SupMat.tex
review
paper

\setcounter{equation}{26}
\setcounter{figure}{7}
\setcounter{table}{3}

@@

>>>>

\setcounter{equation}{25}
\setcounter{figure}{8}
\setcounter{table}{3}

@@

{\color{red}
\section{Application to a Multicomponent Cardiac Signal}
We consider a cardiac signal, namely an arterial blood pressure recording, sampled at $1000$~Hz. In addition to the blood pressure measurement, this signal contains a slow varying component, which is the respiratory component. Fig.~\ref{fig:abp} displays the ordinary and boundary-free SSTs of a 150-second-long extract of this signal, obtained via {\sf BoundEffRed}. This TF analysis brings out both components---the cardiac component, the most energetic, is located around the fundamental frequency $1$~Hz and its multiples, while the respiratory component, less visible, is located around $0.2$~Hz. The performance index of this representation takes the value $D=0.XXX$. Note that, here, boundary effects are only reduced on the right-side boundary of the TF domain. This means that {\sf BoundEffRed} has reduced the right-side boundary effects by about $XX\%$ with respect to the ordinary SST. This shows the ability of our algorithm to work on signals containing several nonstationary components.

\begin{figure}
\centering
%\includegraphics[width=.48\textwidth]{ABPsst.eps}
%\includegraphics[width=.48\textwidth]{ABPberSST.eps}
\caption{Ordinary SST (left) and boundary-free SST (right) of an arterial blood pressure recording}
\label{fig:abp}
\end{figure} 
}

### 2021-01-24 Paper/results.tex
paper

\begin{table}
\centering
\caption{AHM Signal: Performance of the Extension Methods and the Associated Boundary-Free STFT}
\begin{tabular}{|c||c|c||c|}
  \hline
   \multirow{2}{60pt}{\centering Extension method}  & \multirow{2}{30pt}{\centering CPU time (s)} & \multirow{2}{50pt}{\centering MSE\\ (mean $\pm$ SD)} & \multirow{2}{50pt}{\centering Index $D$ of the STFT}\\
    &  & & \\
   \hhline{|=#=|=#=|}
   {\sf SigExt ($M=100$)} & $0.008$ & $1.133 \pm  0.077$ & {\color{blue}$x \pm  x$}\\
   \hline
   {\sf SigExt ($M=750$)} & $0.122$ & $0.479 \pm  0.166$ & {\color{blue}$x \pm  x$}\\
   \hline
   {\sf SigExt ($M=1500$)} & $0.634$ & $0.907 \pm  0.377$ & {\color{blue}$x \pm  x$}\\
   \hline
   {\sf SigExt ($M=3000$)} & $2.881$ & $5.365 \pm  3.919$ & {\color{blue}$x \pm  x$}\\
   \hline
   Symmetric &  $<0.001$ & $5.452 \pm  0.002$ & {\color{blue}$x \pm  x$}\\
   \hline
   EDMD & $1.587$ & $0.983  \pm  0.004$ & {\color{blue}$x \pm  x$}\\
   \hline
   GPR & $515.787$ & $0.479  \pm  0.166$ & {\color{blue}$x \pm  x$}\\
   \hline
   TBATS  & {\color{blue}$x$} & {\color{blue}$x \pm  x$} & {\color{blue}$x \pm  x$}\\
   \hline
\end{tabular}
\label{tab:mse.sine}
\end{table}

@@

>>>>

\begin{table}
\centering
\caption{AHM Signal: Performance of the Extension Methods and the Associated Boundary-Free STFT}
\begin{tabular}{|c||c|c||c|}
  \hline
   \multirow{2}{60pt}{\centering Extension method}  & \multirow{2}{30pt}{\centering CPU time (s)} & \multirow{2}{50pt}{\centering MSE\\ (mean $\pm$ SD)} & \multirow{2}{50pt}{\centering Index $D$ of the STFT}\\
    &  & & \\
   \hhline{|=#=|=#=|}
   {\sf SigExt ($M=100$)} & $0.008$ & $1.133 \pm  0.077$ & $0.0091 \pm  0.0019$\\
   \hline
   {\sf SigExt ($M=750$)} & $0.122$ & $0.479 \pm  0.166$ & $0.0056 \pm  0.0019$\\
   \hline
   {\sf SigExt ($M\!=\!1500$)} & $0.634$ & $0.907 \pm  0.377$ & $0.0065 \pm  0.0023$\\
   \hline
   {\sf SigExt ($M\!=\!3000$)} & $2.881$ & $5.365 \pm  3.919$ & $0.0117 \pm  0.0038$\\
   \hline
   Symmetric &  $<0.001$ & $5.452 \pm  0.002$ & $1.8209 \pm  0.0025$\\
   \hline
   EDMD & $1.587$ & $0.983  \pm  0.004$ & $0.1145 \pm  0.0018$\\
   \hline
   GPR & $515.787$ & $0.479  \pm  0.166$ & $0.0119 \pm  0.0037$\\
   \hline
   TBATS  & {\color{blue}$x$} & {\color{blue}$x \pm  x$} & {\color{blue}$x \pm  x$}\\
   \hline
\end{tabular}
\label{tab:mse.sine}
\end{table}

@@

{\color{red}
Then, we consider a second respiratory signal that contains not only the respiratory cycle, but also the cardiogenic artifact which reflects the hemodynamic component. Fig.~\ref{fig:resp.2} displays the boundary-free SST of a 180-second-long extract of this signal, sample at $125$~Hz, obtained via {\sf BoundEffRed}. This TF analysis brings out both components---the respiratory component, the most energetic, is located around the fundamental frequency $0.25$~Hz and its multiples, while the cardiac component, less visible, is located around $1.7$~Hz. The performance index of this representation takes the value $D=0.314$. Note that, here, boundary effects are only reduced on the right-side boundary of the TF domain. This means that {\sf BoundEffRed} has reduced the right-side boundary effects by about $69\%$ with respect to the ordinary SST. This shows the ability of our algorithm to work on signals containing several nonstationary components.

\begin{figure}
\centering
\includegraphics[width=.48\textwidth]{Resp2comp.eps}
\caption{Boundary-free SST of a two-component respiratory signal.}
\label{fig:resp.2}
\end{figure} 
}
